%-------------------------
% Resume in Latex
% Author : Caio Cavalcante
% Based off of : https://github.com/sb2nov/resume
% https://github.com/jakegut/resume
% https://github.com/arasgungore/arasgungore-CV
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Caio Cavalcante} \\ \vspace{1pt}
    \small
    \faMobile \hspace{.5pt} 
    \href{tel:5575992962199}{+55 (75) 99296-2199}
    $|$ 
    \faAt \hspace{.5pt}
    \href{mailto:x@x.com}{\underline{caio.ca.emp@gmail.com}} 
    $|$ 
    \faLinkedinSquare \hspace{.5pt} 
    \href{https://www.linkedin.com/in/caio-cav-ara}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/caio-cavalcante}{GitHub}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Junior Developer \& IT Support}{Aug. 2024 -- Aug. 2025}
      {Inovare Accounting and Business Consulting}{Feira de Santana, BA, BR}
      \resumeItemListStart
        \resumeItem{Refactored and optimized the institutional website using HTML, CSS, and JavaScript, reducing the total number of lines of code by 15\%, removing redundancies facilitates future maintenance and reduces technical debt;}
        \resumeItem{Responsible for the company's technology sector, including: customer service; diagnosis and troubleshooting; installation, configuration, documentation and maintenance of software;}
        \resumeItem{Developed the website's responsive layout, ensuring a consistent user experience, implemented new features and updated the design to reflect the company's visual identity. Managed the website hosting platform with the content management system (CMS) WordPress;}
        \resumeItem{Structured spreadsheets and analyzed strategic data to generate insights that optimized decision-making and client engagement, converting 5 new companies to the accounting firm;}
        \resumeItem{Presented 20 trainings on the use of new technologies for staff and clients, facilitated technical concepts for internal and external audiences.}
      \resumeItemListEnd

    \resumeSubheading
      {Administrative Assistant}{Oct. 2022 -- July 2024}
      {Inkasa Shop Market 24H}{Feira de Santana, BA, BR}
      \resumeItemListStart
        \resumeItem{Recovered 80\% of the profit lost monthly due to inconsistencies in transactions through auditing processes and data analysis (Excel/Sheets), identifying operational flaws and carrying out proactive collection efforts;}
        \resumeItem{Monitored security cameras in autonomous grocery stores across 15 condominiums;}
        \resumeItem{Used agile methodologies for continuous flow of tasks in the office;}
        \resumeItem{Responsible for customer service.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{IF - Talentos} $|$ \emph{HTML5/CSS3, JavaScript (ES6), PHP 8, PostgreSQL, GitHub}}{Aug. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack platform using PHP and PostgreSQL to create a direct bridge between Information Systems students and the job market, as a potential solution for the high dropout rate and difficulty in obtaining mandatory internships in the academic community;}
            \resumeItem{Implemented the back-end Layered Architecture and the Relational Modeling (SQL) database, ensuring system security with authentication and encrypted passwords, and ecosystem integrity through a curation and approval flow for job postings by administrators;}
            \resumeItem{Designed the front-end interface with HTML, CSS and JavaScript, implementing a multi-profile system (Student, Company, Admin), an administration panel with data visualization to monitor platform health, and a progressive profile system to increase user engagement.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Notification Microservices API} $|$ \emph{Node.js, Express, TypeScript}}{Dec. 2025}
          \resumeItemListStart
            \resumeItem{Developed an isolated RESTful API to manage the sending of transactional emails from the IF-Talentos platform;}
            \resumeItem{Implemented data validation with Zod and integration with an email provider (Resend) to ensure deliverability in production.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Federal Institute of Bahia}{Feira de Santana, BA, BR}
      {Bachelor's degree in Information Systems; GPA: 3.26/4.00 (8.15/10)}{Mar. 2023 -- Mar. 2027}
    \resumeSubheading
      {Helyos International School}{Feira de Santana, BA, BR}
      {High School; GPA: 3.00/4.00 (7.5/10)}{Feb. 2019 -- Nov. 2021}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Technical}{: HTML5/CSS3, TypeScript, React.js, Node.js, Express.js, PostgreSQL.} \\
     \textbf{Developer Tools}{: GitHub, Google Workspace, VS Code, Docker, Figma.} \\
     \textbf{Languages}{: Portuguese (native), English (fluent), Italian e Libras (intermediary).} \\
     }}
 \end{itemize}

%-------------------------------------------
\end{document}